Score-based tests of measurement invariance: Use in practice

### 2013-10-31 frontiers/frontiers.Rnw
Edited index.php to add materials for frontiers paper Related to above, moved files around and deleted some unused files
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/semtools@292 edb9625f-4e0d-4859-8d74-9fd3b1da38cb
Minor changes to make the code more readable, and to ensure that simulations replicate.
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/semtools@293 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

## auxiliary code
source("simall-ordinal.R")
source("mz.R")
source("../www/mz-ordinal.R")

@@

  sim1$nobs <- factor(sim1$nobs)
  levels(sim1$nobs) <- paste("n=", levels(sim1$nobs), sep="")
  levels(sim1$test) <- c("maxLM_O", "WDM_O", "LM_uO")
  save(sim1, file="sim1.rda")
}
sim1$test <- factor(as.character(sim1$test),
  levels = c("ordmax", "ordwmax", "catdiff"),
  labels = c("maxLM_o", "WDM_o", "LM_uo"))
  parlabs <- c(expression(lambda[11]), expression(phi[12]), 
               expression(psi[11]),
	       expression(list(lambda[11], ldots, lambda[62])), 
               expression(list(psi[11], ldots, psi[66])))
  levels(sim1$pars) <- c("Loading1", "Covariance", "Error1", "All Loadings", "All Errors")  
@

>>>>

## auxiliary code
source("../www/sim-frontiers.R")
source("../www/mz-frontiers.R")

@@

  sim1$nobs <- factor(sim1$nobs)
  levels(sim1$nobs) <- paste("n=", levels(sim1$nobs), sep="")
  save(sim1, file="sim1.rda")
}
sim1$test <- factor(as.character(sim1$test), levels = c("ordmax","ordwmax","catdiff"),
                    labels = c("maxLM_o", "WDM_o", "LM_uo"))
parlabs <- c(expression(lambda[11]), expression(phi[12]), 
             expression(psi[11]), expression(list(lambda[11], ldots, lambda[62])), 
             expression(list(psi[11], ldots, psi[66])))
levels(sim1$pars) <- c("Loading1", "Covariance", "Error1", "All Loadings", "All Errors")  
@
